On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-27 engineering.tex
review proof for ports

\begin{definition}{\bf Secure Input Port --}\label{def:secport}
	A secure input port allows information as incoming assertions to flow
	from a sender $s$ to the behavior of the recipient $a$ (agent).  If $p_I$ is a secure input port,
	$\world\models\varphi$, and $\varphi\in\assertionRegion_s$ where $s$
	has the only input port $p_I$, $\world'\models\beliefRegion_a$ and $\varphi\in\beliefRegion_a$.
\end{definition}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\circ\rightarrow a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\rightarrow\bullet a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\circ\rightarrow\bullet a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port} ($s\hookrightarrow a$), where some
		information passes the port while other is either dropped
		($s\circ\hookrightarrow a$), inserted
		($s\hookrightarrow\bullet a$), or injected
		($s\circ\hookrightarrow\bullet a$)
\end{itemize}

@@

>>>>

\begin{definition}{\bf Secure Input Port --}\label{def:secport}
	A secure input port allows information as incoming assertions to flow
	from a sender $s$ to the behavior of the recipient $a$ (agent).  If $p_I$ is a secure input port,
	$\world\models\varphi$, and $\varphi\in\assertionRegion_s$ where $s$
	has the only input port $p_I$, $\world'\models\beliefRegion_a$ and $\varphi\in\beliefRegion_a$.
\end{definition}

\Paragraph{Port weaknesses}
From this definition, it follows that there exist only the following types of insecure port in RCC5:
\begin{itemize}
	\item \emph{drop port} ($s\dropport a$), where assertions reaches the port but do not pass the boundary of the agent (i.e. do not become belief of the agent)
	\item \emph{insertion port} ($s\insertport a$), where some new information is believed by $a$ as incoming from the port but $s$ didn't send it
	\item \emph{injection port} ($s\injectionport a$), where information coming from $s$ is substituted with new information which becomes believed by $a$
	\item \emph{selective port}, where some
		information passes the port while other is either dropped
		($s\selectivedropport a$), inserted
		($s\selectiveinsertport a$), or injected
		($s\selectiveinjectionport a$)
\end{itemize}

@@

An input port is, in the $\abf$-theory, defined secure as long as the relation
	between the two regions of input assertions $\assertionRegion$ and
	output beliefs $\beliefRegion$ are equal, i.e.
	$\eq{\assertionRegion}{\beliefRegion}$. Therefore, any other relation
	should result in a weakness (related to an insecurity flaw) of that
	input port.  Using RCC5, there exist exactly other $4$ different type
	of relations, one of which is the discrete-from (DR) relation, i.e.
	$\dr{\assertionRegion}{\beliefRegion}$. When two regions are related by
	the DR relations, they have no subregion in common. Lets
	define a function weight $|X|$ such as, for any region $X$, it
	represents the smallest possible cardinality of a (mereo)topological base for
	$X$; where a base is a collection of regions in a (mereo)topology such that
	every open region can be written as union of elements of that base.  If
	a communication occurred and results in
	$\dr{\assertionRegion}{\beliefRegion}$, there exist only two mutually
	exclusive options: either $|\assertionRegion|=|\beliefRegion|$ or
	$|\assertionRegion|\neq|\beliefRegion|$. 
	\begin{itemize}
		\item If $|\assertionRegion|\neq|\beliefRegion|$ (at the end of
			a communication through the input-port), the two
			regions have a different number of subregions, and,
			then, there exist only two mutually exclusive options: 
			\begin{itemize}
				\item either $|\assertionRegion|>|\beliefRegion|$, where one
					ore more Assertions didn't become Beliefs, which we
					call \emph{drop port} ($s\dropport a$) since its behavior drops and
					prevents incoming communications,
				\item or $|\assertionRegion|<|\beliefRegion|$, where there are
					one ore more Beliefs which have not been sent as
					input-Assertions, which we call \emph{insertion
					port} ($s\insertport a$) since its behavior generates new Beliefs
					unrelated to the incoming communication. 
			\end{itemize}
		\item If $|\assertionRegion|=|\beliefRegion|$, supposing an increasing monotonic entropy on the information (Assertions) exchanged, 
				there exist only two mutually exclusive options: 
			\begin{itemize}
				\item either information has been generated as Belief and transferred as Assertions, increasing the cardinality of both
					$\assertionRegion$ and $\beliefRegion$, i.e.
					$|\assertionRegion_{t^0}|>|\assertionRegion_{t^1}|$ and
					$|\beliefRegion_{t^0}|>|\beliefRegion_{t^1}|$ (where
					$t^0$ and $t^1$ represent time at the beginning of
					communication and right after, respectively); which
					means that Assertions have reached the port and new
					Beliefs have been generated by the port, but no
					correlation between the elements of the two regions exist. 
					We call this \emph{injection port} ($s\injectionport a$) since it has modified
					the information carried by the Assertions into new
					corresponding Beliefs.
				\item or $|\assertionRegion_{t^0}|=|\assertionRegion_{t^1}|$
					and $|\beliefRegion_{t^0}|=|\beliefRegion_{t^1}|$ but
					this implies that no communication occurred, while we
					assumed that a communication was taking place (absurd).
			\end{itemize}
	\end{itemize}
	Similarly, 
	\begin{itemize}
		\item given that $\po{\assertionRegion}{\beliefRegion}$ is equivalent to
			$\dr{\assertionRegion}{\beliefRegion}$ except for the
			overlapping part (see Appendix~\ref{app:selectiveinjectionport}) in which case is
			$\eq{\assertionRegion}{\beliefRegion}$ (see
			\autocite{Santaca2016abf}),
			we call it a \emph{selective injection port} ($s\selectiveinjectionport a$); otherwise
		\item $\pp{\assertionRegion}{\beliefRegion}\equiv\assertionRegion\Leftarrow\beliefRegion$ and
			$\ppi{\assertionRegion}{\beliefRegion}\equiv\assertionRegion\Rightarrow\beliefRegion$ are subcases of
			$\eq{\assertionRegion}{\beliefRegion}\equiv\assertionRegion\Leftrightarrow\beliefRegion$, and then
		\begin{itemize}
			\item if $\pp{\assertionRegion}{\beliefRegion}$, we have that
				some Beliefs are not correlated to incoming Assertions
				and we call it \emph{selective insertion port} ($s\selectiveinsertport a$),
			\item if $\ppi{\assertionRegion}{\beliefRegion}$ we have that
				some incoming Assertions are not correlated to Belief 
				and we call it \emph{selective drop port} ($s\selectivedropport a$)
		\end{itemize}
	\end{itemize}
